\begin{position}
  {
    title   = Software Systems Architect,
    company = Epic Systems,
    company-link = https://www.epic.com,
    date    = Jun 2015-*,
    city    = Verona,
    state   = WI,
    technical,
  }

  On the Software Delivery team since June 2021. Within a quarter of
  transfer, became project direction lead and the team's de-facto Git
  expert for SVN to Git migration for $\approx 3,000$ software
  developers. 80\% of source control activity is to a multi-trunk
  (patch promotion) monorepo of over 6\,million commits across $>15$
  years.
  % While we use \software{GitLab} as the repository host, we do not
  % use its workflows, opting instead to implement our own for quality
  % and regulatory reasons to integrate with existing quality tracking
  % and release processes.
  %
  \emph{Designed all the fundamentals} of developer workflows while
  integrating into our existing quality tracking and software delivery
  processes. \emph{Fostered developer ownership} in the larger team
  after meeting proof-of-concept and getting \emph{leadership buy-in}
  based on normalized estimates and comparative cost analysis.

  \medskip

\begin{itemize}
  \def\importantpoint{{\large$\star$\hspace*{-1pt}}}
\item Identified and averted multiple disaster scenarios within first
  weeks after transfer.
% patch-based merges to St1/Final
%
% security vulnerabilities in trusting client hooks
%
% BM0 (SVN+Git)
%
% BM1 (SVN|Git)
\item Designed a standard pull request / merge queue workflow using
  pure Git functionality sitting atop pre-existing database
  infrastructure. New workflow improved end-user developer performance
  perception \emph{from minutes\slash hours to $<10$ seconds}.
%\item Designed a minimal and stable cherry-pick process to promote
%  changes.
\item[\importantpoint] Designed, prototyped, and handed off a new
  infrastructure for our developer tooling~-- built from the ground up
  to teach people how to use Git well.
\item Git technical expert for our custom SVN replay solution.
\item Designed and implemented automated integrated testing solution,
  creating an easy-to-use, extensible system and handing it off to
  others for most maintenance.
\item Designed, generated, and consulted for end-user developer
  training materials: video demos, written lessons, and written
  projects/exams.
\item Taught internal support team the necessary knowledge of Git
  internals and the major components of our system in order to provide
  effective support to developers.
\item Designed and implemented comprehensive developer documentation
  solution using unfamiliar technologies~-- getting \emph{leadership
    buy-in} to move away from MediaWiki.
\item Identified performance optimizations for downloading
  pre-compiled binaries using tools not yet used by the team
  \emph{resulting in a $>10\%$ time savings}.
\item During a company-wide performance escalation, spent two days to
  independently identify new opportunities for savings. Prototyped a
  tool to \emph{reduce size of all delivered stylesheets by $11\%$}
  using unfamiliar technologies.
\end{itemize}

\medskip
\hrule
\medskip

Six years working on a clinical application. Full-stack developer
working with \censor{M} and \censor{VB6} transitioning to a
\censor{new}, \censor{proprietary} \censor{ASP.NET}-based platform
(\censor{M}, \CSharp, JS, and TS), designing with customers for the
future while keeping them successful in their existing implementation.
Our software is the \censor{nervous system} for \censor{healthcare
  providers} both domestic and abroad \Dash with records for well over
half the U.S. population.

  \medskip

\begin{itemize}
  \def\importantpoint{{\large$\star$\hspace*{-1pt}}}
\item Maintain and extend a complex NoSQL database with multiple
  concurrently-supported versions.  Implement multiple data model
  conversions to support current and future technical needs
  (\censor{M}).
\item Responsible for a major integrated component of our software
  over entire tenure \Dash with many projects spanning the course of
  several months (\censor{M}, \censor{VB6}, \CSharp, JS, TS).
%\item Work closely with other teams to provide a consistent user
%  experience.
\item Work with core infrastructure teams to design and implement
  developer tooling \Dash including \censor{a new TypeScript-based
    language that compiles to M}.
%\item[\importantpoint] Lead a cross-role effort to streamline our
%  team's use of automated testing and overcome technical challenges
%  specific to our domain.  Establish team-wide processes.
%\item[\importantpoint] Establish team-wide processes to ensure our
%  customers receive high-quality out-of-the-box configuration.
%\item[\importantpoint] Develop and teach a curriculum based on
%  \CSharp\ for co-workers with no prior experience.
\end{itemize}
\end{position}

% Local Variables:
% TeX-master: "../../cv.tex"
% End:
