% arara: xelatex
% arara: make: { task: "cv.png" }
\documentclass{simplecv}
\BetterSetup{
  textout = \jobname.cv.txt,
  textout-preamble = preamble.txt,
}
%\CensorInformation

\usepackage{additional-setup}
\usepackage{ragged2e}

\ContactInformation{
  name   = Dolan Duck,
  email  = dolanduck@tex.stackexchange.com,
  url    = http://tex.stackexchange.com,
  phone  = 123\,456\,7890,
  street = 123 Duck Lane,
  city   = Duckville,
  state  = Duckota,
  zip    = 211 145 63,
}

\newif\ifmath
\newif\ifgithub
\newif\ifinterests

\IfCensoredTF{}{\IfFileExists{./contact-info.tex}{\input{contact-info}}{}}

\mathtrue
\githubtrue
\intereststrue

\begin{document}
\maketitle
\vfill
\section{Technical Summary}
\begin{minipage}{\textwidth}
\begin{description}
\item[Languages]
  C,
  \CPP,
  Objective~C,
  \CSharp\,.NET,
  Java,
  Visual\,Basic~.NET,
  VB6,
  \censor{M},
  Python,
  Bash,
  \software{Mathematica},
  \software{Emacs}~\Lisp\slash
            Common~\Lisp\slash
            Scheme,
  SQL,
  \TeX,
  and
  \texttt{expl3}

\item[Software]
  \software{Emacs},
  \software{\cli{git}},
  Microsoft \software{Word},
            \software{Excel},
            \software{Powerpoint},
            \software{Publisher},
            \software{OneNote},
            \software{Visio},
            and
            \software{Outlook},
  Adobe's
    \software{After Effects},
    \software{Premiere Pro},
    \software{Audacity},
  \software{Redmine},
  \software{Eclipse},
  \software{Travis\,CI},
  \software{Wordpress},
  and
  \software{Visual Studio 2008\,--\,2013}

\item[Operating Systems]
  Windows~7+,
  Mac OS\,X,
  and
  Red\,Hat Enterprise~Linux 5\slash 6

\item[Communication]
  Excellent communication skills, both written and oral,
    with experience in literate programming
\end{description}
\end{minipage}

\vfill
\section{Education and Academic Experience}
\begin{education}
  {
    major = Computer Science,
    degree = BA,
    gpa = 3.6,
    major-gpa = 3.9,
    school = St. Mary's College,
    school-link = http://www.smcm.edu/mathcs,
    state = MD,
    city = Lexington Park,
    transcript = \transcript,
    date = 2010-2014,
  }

\begin{description}
\item[Coursework]
  \course{Data Structures and~Algorithms},
  \course{Design and~Analysis of~Algorithms},
  \course{Theory of Computation},
  \course{Programming Languages},
  and
  \course{Small-Scale Computing}
\item[Honors] Dean's List ($\text{\Acronym{GPA}} \geq 3.5$) each semester;
  Senior Award in Computer Science
\item[Research] Worked under \censor{Dr.~Alan~Jamieson} in simulating
  self-stabilizing algorithms.
  \\
  See \url{http://github.com/vermiculus/ssa-tool}.
\item[Abroad] Studied abroad at \href{http://www.ucd.ie}{\censor{University College Dublin}} in the \censor{Republic of~Ireland}.
  Worked with \censor{Dr.~P\'adraig~Cunningham} researching named-entity recognition and social network
  analysis in English literature. (\dates{Jan-May 2013})
  \\
  See \url{http://github.com/vermiculus/snael}.
\end{description}
\end{education}

\begin{position}
  {
    print   = false,
    title   = Minor \Dash Mathematics,
    company = St. Mary's College,
    company-link = http://www.smcm.edu/mathcs,
    date    = 2010-2014,
    state   = MD,
    city    = Lexington Park,
    title-link = \transcript,
  }

  \begin{description}
  \item[Key Courses]
    \course{Set Theory},
    \course{Calculus I, II, III},
    \course{Real Analysis},
    \course{Metric Spaces},
    \course{Abstract Algebra},
    and
    \course{Operations Research}
  \end{description}
\end{position}

\begin{position}
  {
    print   = false,
    title   = Teaching Assistant,
    company = St. Mary's College,
    company-link = http://www.smcm.edu/mathcs,
    city    = St. Mary's City,
    state   = MD,
    date    = 2011-2014,
  }

\begin{itemize}
\item Mentor students in object-oriented design, data structures, algorithms, computer architecture, and programming languages.
\item Organize and conduct weekly review sessions.
\item Regularly grade small projects and assignments.
\item Created written tutorials in course concepts for students in CS~I\slash II.
\end{itemize}
\end{position}

\section{Professional Experience}

\begin{position}
  {
    title   = Software Developer,
    company = Epic Systems Corporation,
    company-link = http://www.epic.com,
    date    = Jan 2015-*,
    city    = Verona,
    state   = WI,
    technical,
  }

\begin{itemize}
\item To be determined\dots
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Junior Software Dev.,
    company = General Dynamics,
    company-link = http://www.gd-ais.com,
    date    = June 2014-Jan 2015,
    city    = Fairfax,
    state   = VA,
    technical,
  }

\begin{itemize}
\item Maintained and enhanced existing software solution using X~programming.
\item Redesigned graphical system to adhere to best practices in object-orientism.
\item Consolidated duplicated functionality and polished an NFS mount manager.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Server Administrator,
    company = St. Mary's College,
    company-link = http://www.smcm.edu/mathcs,
    date    = Sept 2013-May 2014,
    city    = St. Mary's City,
    state   = MD,
    technical,
  }

\begin{itemize}
\item Prepared and implemented an authenticated documentation server using \href{http://www.redmine.org}{Redmine}.
\item Maintained the hardware, software, firewalls, and other security measures
  for the department's subnetwork of 10\,--\,15 servers (both physical and virtual) via remote Linux administration using \texttt{ssh}\slash PuTTY.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Intern,
    company = {Progeny Systems, Inc.},
    company-link = http://progeny.net,
    date    = May-Sept 2013,
    city    = California,
    state   = MD,
    technical,
  }

\begin{itemize}
\item Created, documented, and maintained several virtual systems
  and virtualized existing infrastructure systems with vSphere\slash KVM via primarily remote Linux administration.
%\item Generated a skeleton graphical interface to a \textsc{cli} (YASCA) with Java.
\item Independently responded to and resolved non-critical emergency situations swiftly
  with minimal down-time or impact to end-users.
%\item Acquired expository experience for a range of topics including
%  networks,
%  databases,
%  server setup, and
%  remote administration.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Student Technician,
    company = St. Mary's College,% \Dash Office of Information Technology,
    company-link = http://oit.smcm.edu,
    city    = St. Mary's,
    state   = MD,
    date    = 2010-2013,
  }

\begin{itemize}
\item Supported clients in the use of the network and their software,
  troubleshooting both software and hardware problems on both Windows (Dell) and Apple computers.
\item Inventoried and organized departmental property.
\item Prepared aged hardware for release within state security specifications.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Software Developer,
    company = Capital Women's Care,
    company-link = http://www.cwcare.net,
    city    = Silver Spring,
    state   = MD,
    date    = 2008-2011,
    print   = false,
    technical,
  }

\begin{itemize}
\item Formalized and removed ambiguities to establish and document project scope.
\item Developed and maintained several \CSharp\,.NET applications to
  improve hiring workflow for multiple offices in the tri-state area.
\end{itemize}
\end{position}

\vfill \vfill
\newpage~\vfill

\section{Personal Information}
\begin{itemize}
\item Experienced user of \LaTeX, a system used to produce documents
  of high quality and typographical consistency.
\item Currently an official representative of
  \href{http://meta.tex.stackexchange.com/a/4174/17423}{StackExchange}
  to the international \href{http://www.tug.org}{\TeX\ User's Group}.
\item Contributed \TeX\ extension packages to CTAN.
\item Edited and produced a promotional video for a \href{http://www.smcm.edu/desousabrent}{diversity program} at \censor{St. Mary's College} (archived).
\item Maintain\slash contribute to several
  \href{http://www.github.com/vermiculus}{open-source projects}
  using more conventional languages, such as
  \software{Emacs}~\Lisp, Python, Java, C, and Objective~C.
  (Contributions range from testing to discussion to design to program code.)
\end{itemize}

\ifgithub
\vfill
\section{Open Source Contributions \hfill \Embrace{\ttfamily github.com/vermiculus}}

\project{
  title       = StackAPI,
  description = Language-native method stub and type generation using a scraped API,
  date        = 2014-*,
  ghkey       = vermiculus/stack-api,
  link        = https://www.github.com/vermiculus/stack-api,
  technology  = {XML, XSLT, XSD, XPath, Python}
}

\project{
  title       = \cli{sx.el},
  description = An ongoing project to create a full-featured StackExchange mode for \software{Emacs},
  date        = 2013-*,
  ghkey       = vermiculus/sx.el,
  link        = https://www.github.com/vermiculus/sx.el,
  technology  = \software{Emacs} \Lisp,
  technical,
}

\project{
  title       = \cli{ssa-tool},
  description = An editor for and simulator of self-stabilizing algorithms,
  date        = 2013-*,
  ghkey       = vermiculus/ssa-tool,
  link        = https://www.github.com/vermiculus/ssa-tool,
  technology  = {Python, NetworkX, PyYAML},
  technical,
}

\project{
  title       = \Acronym{SNAEL},
  description = A natural language analyzer that constructs social networks,
  date        = Jan-May 2013,
  link        = https://github.com/vermiculus/snael,
  ghkey       = vermiculus/snael,
  technology  = Python,
  technical,
}

\project{
  title       = MobileOrg,
  description = An asynchronous iOS complement to \software{Emacs}' OrgMode,
  link        = https://www.github.com/mobileorg/mobileorg,
  ghkey       = MobileOrg/mobileorg,
  date        = May-May 2013,
  technology  = Objective C,
  technical,
}

\project{
  title       = \AucTeX-Lua,
  description = An extension to \AucTeX\ to support embedded Lua code,
  link        = https://www.github.com/vermiculus/auctex-lua,
  ghkey       = vermiculus/auctex-lua,
  date        = Aug-Aug 2013,
  technical,
  technology  = \software{Emacs} \Lisp,
}

\project{
  title       = ButterSeal,
  description = An Android game written for \course{Game Design and Development},
  date        = Sept-Dec 2013,
  link        = https://www.github.com/vermiculus/butterseal,
  ghkey       = vermiculus/butterseal,
  technical,
  technology  = (LibGDX) Java,
}

\project{
  title       = C-\textsc{util},
  description = A set of object-oriented utilities for ANSI C,
  link        = https://www.github.com/vermiculus/c-utils,
  ghkey       = vermiculus/c-util,
  technical,
  technology  = C,
  date        = 2012-*; Stagnant
}

\project{
  title       = LDA\slash SMC Website,
  description = A new website for the local Learning Disabilities Association,
  link        = http://www.ldasmc.org,
  technology  = {\textsc{WordPress}, discountASP},
  date        = March 28-30 2013,
}

\project{
  print       = false,
  title       = \Acronym{BITS},
  description = The Binary Integer Transformation System: a compression algorithm,
  technical,
  technology  = C,
  date        = 2012-*
}
\fi

\ifinterests
\section{Relevant Interests}
I have several interests in which I have no formal training,
  but have significant experience.
These include:
\vfill

% This hackery was to make the two columns different widths.
% Normally, you should use multicol or vwcol to make multiple columns.
\begin{minipage}[t]{0.55\linewidth}
  \begin{itemize}\RaggedRight
  \item structured documents, especially in the context of $\downarrow$
  \item literate programming \Dash a documentation-centric paradigm
    for software development and reproducible research,
  \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\linewidth}
  \begin{itemize}
  \item custom electronics, and
  \item typography.
  \end{itemize}
\end{minipage}
\vfill

\centering
Additional details on my projects and interests can be found at
  \url{http://www.seanallred.com}.
\fi
\vfill
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% TeX-command-default: "arara"
%%% TeX-engine: xetex
%%% End:

%  LocalWords:  gpa adraig Jamieson Mathematica Powerpoint OneNote
%  LocalWords:  JSON cli YASCA Camtasia tri PDF PostgreSQL Visio CTAN
%  LocalWords:  Visio Redmine company-link title-link StackExchange
%  LocalWords:  StackMode ghkey vermiculus
